---
title: "Homework 3, DACSS 690D"
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-github", href: "https://github.com/DACSS-Spatial/The-Thematics", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}

In Iowa, vacancy in the housing stock reflects broader dynamics in the state’s real-estate market. According to recent data, the overall average housing vacancy rate across the state is around 9.6%, meaning nearly one in ten housing units is not currently occupied. Rental vacancy rates are also notable, with Iowa recording a rental vacancy rate near 8.0% in 2024. 

Vacant homes and buildings have mixed implications: while some vacancies can signal available housing supply, high vacancy levels can also depress property values and create concerns about community safety and under-utilized structures—prompting local programs aimed at revitalization and maintenance. 

At the same time, Iowa faces housing supply challenges, particularly in affordable and workforce housing segments, where shortages persist in many counties. This shortage can keep vacancy from translating into real relief for renters and buyers, as many vacant units are not suitable or affordable for local demand.

The Repo that generated this dashboard can be found [here!](https://github.com/meade68/DACSS_690D_Week13_HW3)

## Column {.tabset .tabset-fade}

### Housing Vacancy, K-Means Clusters (Non-Spatial) 

```{r}
readRDS(url("https://github.com/meade68/DACSS_690D_Week13_HW3/raw/refs/heads/main/Iowa_K5.rds"))
```

### Housing Vacancy, SKATER Clusters (Spatially Constrained)

```{r}
readRDS(url("https://github.com/meade68/DACSS_690D_Week13_HW3/raw/refs/heads/main/Iowa_SkaterR.rds"))
```

